CommonMind Consortium: DLPFC

### 2020-09-17 combined_analysis/diff.networks.Rmd
Update diff networks

knitr::opts_chunk$set(
  echo = FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```

@@

dynamicColors = labels2colors(dynamicMods, colorSeq = colors())
tab = table(dynamicColors)
length(tab)

@@

>>>>

knitr::opts_chunk$set(
  echo = FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE,
  cache.lazy = FALSE)
```

@@

dynamicColors = labels2colors(dynamicMods, colorSeq = colors())
tab = table(dynamicColors)
length(tab)
```

```{r testing}

@@

Can we predict sex given autosomal genes?

PMID: 26892004
https://science.sciencemag.org/content/369/6509/eaba3066
https://www.nature.com/articles/s41576-018-0083-1

test: how much sex differences are given by age, cell type and institution.
